---
title: "First Map V1.0"
subtitle: "GLOBAL OVERVIEW OF POSTNATAL CARE FOR NEWBORNS"
author: "Olha Volodko"
date: "2024-04-01"
format: 
  html:
    theme: sandstone
    toc: true
  
execute:
  echo: false
  warning: false
  message: false
  

---

```{r}
#| labal: setup
#| include: false

# libraries
library(tidyverse)
library(rnaturalearth)
library(sf)
library(readr)
library(scales)
library(plotly)
library("gridExtra")

# data
unicef_metadata <- read_csv("unicef_metadata.csv") 
unicef_indicator_2 <- read_csv("unicef_indicator_2.csv") 

# transformations
merged_data <- unicef_metadata %>%
  inner_join(unicef_indicator_2, by = c("country", "year" = "time_period"))
```
#INTRODUCTION:


The comprehensive study covers <span style="color: red; font-weight: bold;">109 countries</span>, delving into the intricate web of factors influencing postpartum care. Key indicators such as GDP, education spending, and health expenditure are scrutinized, providing insights into their perceived impact on postnatal care. This narrative unfolds the global landscape of postnatal care for newborns, leveraging data spanning from 2010 to 2022.

```{r}
#| fig-cap: GLOBAL OVERVIEW OF POSTNATAL CARE FOR NEWBORNSGLOBAL OVERVIEW OF POSTNATAL CARE FOR NEWBORNSGLOBAL OVERVIEW OF POSTNATAL CARE FOR NEWBORNSGLOBAL OVERVIEW OF POSTNATAL CARE FOR NEWBORNS
#| 
# Load data
unicef_indicator_2 <- read_csv("unicef_indicator_2.csv") 

# Calculation of the average post-natal care rate
average_care <- unicef_indicator_2 %>%
  group_by(alpha_3_code) %>%
  summarise(avg_postnatal_care = mean(obs_value, na.rm = TRUE))

# Load map data
world <- ne_countries(scale = "medium", returnclass = "sf")

# Merging of average postpartum care data into world map data
world_with_data <- left_join(world, average_care, by = c("iso_a3" = "alpha_3_code"))

# Add a custom text column to the dataframe for plotly's mouseover text
world_with_data <- world_with_data %>%
  mutate(hover_text = sprintf("Country: %s\nAvg Postnatal Care: %.2f%%", name, avg_postnatal_care))

# Creating ggplot plots, referencing custom text
m <- ggplot(data = world_with_data) +
  geom_sf(aes(fill = avg_postnatal_care, text = hover_text)) + # Use text aesthetic to reference hover_text
  scale_fill_gradient(low = "#FFCCCC", high = "#E15252", name = "Avg Postnatal Care (%)") +
  labs(title = "Average Postnatal Care Percentage by Country",
       subtitle = "Percentage of newborns receiving postnatal care") +
  theme_minimal() +
  theme(legend.position = "bottom")

# Converts ggplot plots to interactive plotly plots, specifying the use of custom mouse hover text
interactive_m <- ggplotly(m, tooltip = "text")

# Displaying Interactive Charts
interactive_m
```

